About the job
Hi,



Kollin helps engineering students with their studies. Our platform transforms static academic content into engaging, interactive experiences. Our mission is to boost student success and retention in STEM fields by giving students what they need: tools from 2024. Founded by passionate engineers, Kollin has already captured a significant market share among Swedish universities. We're now poised for rapid growth and innovation as we have gotten grants by Vinnova to build an adaptive learning system with the help of AI.



We're seeking a Full Stack Engineer with a few years experience to help us strengthen our tech team, build features and make sure our app stays ahead of its competitors.



Some of the things we will work on:

• Automated content processing pipelines

• LLM integration for personalized learning

• Interactive learning tools and rich editors

• User dashboards and adaptive study plans

• Community features and AI-assisted tools



Our tech stack includes:

• Frontend: Next.js, React

• Backend: Node.js, GraphQL

• Database: Neon, RDS

• Infrastructure: AWS, Microservices, Vercel



Skills and experience:

• 3+ years of professional web development experience

• Strong skills in JavaScript/TypeScript and React

• Experience with Node.js and GraphQL APIs

• Familiarity with AWS services and microservices architecture

• Passion for education and AI technologies



We hope that you are as passionate as we are to building great tools for learning. There is so much happening in this space right now and we want to work with other tech enthusiasts who can see all there is to do in the AI for learning space.



Looking forward to hearing from you!