About the job
As one of a few companies worldwide, we have solved the tough problem of bringing data science to production while keeping costs and operations at bay. We will continue to relentlessly drive innovation to pursue our vision of the autonomous supply chain. On the way, we have solved, and will solve plenty of interesting and challenging problems, and we would love to have you on board for that journey.

What To Expect

Work in an experienced team with our machine learning experts, engineers and project managers to advance our data science products
Design and develop data-intensive distributed systems in Python with focus on data engineering
Design and develop UI to visualize machine learning forecasts
Work in an agile team with emphasis on quality, testability and automation

Your Experience

Passion for building reliable software running in production. In-depth knowledge in one of the following areas and ambition to advance in the others:

Python and its ecosystem around pandas and sqlalchemy
Modern JavaScript library like React, Vue.js or Angular
Micro-services architectures in cloud environments

Every day, our teams work enthusiastically with our customers on innovative AI-based solutions and sophisticated optimization for the retail industry. Working with us means you can look forward to co-workers who use creativity to collectively develop ideas and appreciate each other’s expertise.

We live for pushing artificial intelligence forward and scalable solutions. Joining our team means you can look forward to working with our people on realising creative ideas and see how they operate in the resulting solutions. Mutual respect, friendly relationships and results-oriented work are an important part of our environment. We strive to be a family-friendly business and are open to modern working structures.

We believe that the individuality and diversity of our employees make a decisive contribution to our success. Our hiring process is based on qualifications and career profile. We welcome applications from all motivated candidates, regardless of age, gender, disability, sexual orientation, origin or religion.

Our Values

If you want to know the heart of a company, take a look at their values. Ours unite us. They are what drive our success – and the success of our customers. Does your heart beat like ours? Find out here: Core Values