About the job
About the Company: Oeson is a leading IT corporation globally recognized for its expertise in providing top-notch IT and Ed-tech services. Specializing in digital marketing, data science, data analytics, UI-UX design, web development, and app development, we are dedicated to innovation, excellence, and empowering talents worldwide.

Learn More: www.oesonlearning.com



Job Summary:



Oeson is seeking enthusiastic individuals who are looking to learn with us in the field of Data Science while working on live projects internationally. We are not just offering a flexible work environment but also offering to work with people in a global team.



Projects You Will Work On:



- Finance Fraud Detection: Develop advanced fraud detection algorithms leveraging financial data analysis.

- Recommender System: Contribute to personalized recommendation systems, enhancing user experiences across platforms.

- Sentiment Analysis: Explore sentiment analysis to extract insights from textual data, shaping user sentiment understanding.

- Chatbots: Engage in intelligent chatbot development, revolutionizing customer interactions and support.

- Image/Audio Video Classification: Push boundaries with multimedia technology by working on image and audio video classification projects.

- Text Analysis: Uncover hidden patterns in textual data through sophisticated text analysis techniques.



Roles & Responsibilities:


- Collaborate with our esteemed data science experts to collect, clean, and analyze extensive datasets, honing skills in data preprocessing and visualization.

- Contribute to the development of predictive models and algorithms, employing cutting-edge machine learning techniques to solve real-world challenges.

- Work closely with team members to design, implement, and evaluate experiments, fostering a collaborative and innovative environment.

- Stay updated with the latest industry trends and best practices in data science, applying newfound knowledge to enhance project outcomes.



Qualifications:



- Currently pursuing any degree showcasing a strong commitment to continuous learning and professional growth.

- Exceptional written and verbal communication skills, vital for effective collaboration and articulation of complex ideas.

- Demonstrated ability to work both independently and as part of a cohesive team, highlighting adaptability and strong teamwork capabilities.



Note:



This position is unpaid. After submitting your application, our team will contact you to proceed with the application details and joining process.



Location:

Remote, European Union