Germany (Hybrid)
The team you'll be part of 

Our Business Group is a leader in wireless mobility networks and associated services. With 
more than 3.500 patent families essential for 5G we have a strong 5G portfolio and are a front 
runner in open and virtualized radio access networks (O-RAN and vRAN). 
You will be working in the 5G L3 SW Development in Ulm joining a highly motivated intercultural 
team. Together we are creating the (L3) control plane SW of the Nokia 5G New Radio base station. 
We celebrate a culture of collaboration and openness. By that we fearlessly address 
any challenge to improve what we are doing and how we are doing it.   


 

HOW YOU WILL CONTRIBUTE AND WHAT YOU WILL LEARN
What you will learn and contribute to 

As a Software Development Engineer, you and your team will implement and verify the latest 
features for the Nokia 5G product family in self-organized SCRUM teams.
Your focus will be on Layer 3 related protocols and resource management within the 5G gNB.  
As part of our team, you will: 

design, implement and maintain high availability SW for 5G base station embedded systems   
refine, estimate and plan the work for the next sprint with your team  
ensure quality by defining and implementing unit- and component-test and taking part in code reviews   
analyze and correct software defects

 
KEY SKILLS AND EXPERIENCE
 Your skills and experience 

  You have: 

basic understanding of 5G New Radio or LTE channels, protocols and procedures  
solid knowledge of Python and C++14 (and beyond)  
experience in developing software in a Linux environment, Bash scripting, IT network and SW debugging.    
master's or bachelor’s degree in electrical engineering, telecommunication, computer science
good communication skills in English (both written and spoken)
 It would be nice if you also had:  

passion for cooperative Teamwork and Agile Software Development processes  
worked with git, gerrit, gtest, gmock, continuous integration systems 
knowledge of Clean Code and the SOLID Principles  
first experiences with software test concepts like unit test, component test,
test-driven development (TDD), continuous integration (CI), test automation skills  
About Us
Come create the technology that helps the world act together

Nokia is committed to innovation and technology leadership across mobile, fixed and cloud networks. Your career here will have a positive impact on people’s lives and will help us build the capabilities needed for a more productive, sustainable, and inclusive world.
We challenge ourselves to create an inclusive way of working where we are open to new ideas, empowered to take risks and fearless to bring our authentic selves to work

What we offer
 
Nokia offers continuous learning opportunities, well-being programs to support you mentally and physically, opportunities to join and get supported by employee resource groups, mentoring programs and highly diverse teams with an inclusive culture where people thrive and are empowered.

Nokia is committed to inclusion and is an equal opportunity employer

Nokia has received the following recognitions for its commitment to inclusion & equality:

One of the World’s Most Ethical Companies by Ethisphere
Gender-Equality Index by Bloomberg
Workplace Pride Global Benchmark

At Nokia, we act inclusively and respect the uniqueness of people. Nokia’s employment decisions are made regardless of race, color, national or ethnic origin, religion, gender, sexual orientation, gender identity or expression, age, marital status, disability, protected veteran status or other characteristics protected by law.
We are committed to a culture of inclusion built upon our core value of respect.

Join us and be part of a company where you will feel included and empowered to succeed.
About the Team
Our Business Group is a leader in wireless mobility networks and associated services. With more than 3.500 patent families essential for 5G we have a strong 5G portfolio and are a front runner in open and virtualized radio access networks (O-RAN and vRAN). 
