About the job
About Us: At ValueWorks, we empower businesses to unlock their full potential through cutting-edge data analytics, functionalities and AI-driven insights, leveraging the data from operational systems like CRM, ERP and others. 

 

Our team of industry experts and data scientists work closely with clients to understand their unique challenges and craft tailored solutions that provide a competitive edge. 

Discover how ValueWorks can help your business thrive in the digital age. Visit us at ValueWorks.ai to learn more. 

 

Job Description: We are looking for a Full Stack Developer who is proficient in React.js and Django to join our team. You will be responsible for building and maintaining a part of our web applications, working on both the front-end and back-end. Experience or familiarity with Go is a plus, as a part of our back-end is written in Go. 

 

Responsibilities: 

Developing and implementing UI components using React.js 
Collaborating with cross-functional teams to design and ship new features 
Building reusable components and front-end libraries for future use 
Translating designs and mock-ups into high-quality code 
Optimizing components to maximize performance across various web browsers 
Staying up-to-date with the latest industry trends and technologies 
Troubleshooting and debugging issues to ensure smooth user experiences 
Participating in code reviews to maintain code quality and consistency 
Contribute to Go-based services and projects, as needed (Go experience is a plus). 
 

Requirements: 

Proficiency in React.js (v17+) and its core principles 
Strong HTML5, CSS3, and Typescript skills 
Experience with popular React.js workflows (such as Redux or similar libraries) 
Familiarity with RESTful APIs and testing mechanisms for Front-end (such as Jest or Vitest) 
Knowledge of modern authorization mechanisms, such as JSON Web Tokens (JWT) 
Understanding of front-end build tools and pipelines 
Excellent problem-solving and communication skills 
A strong attention to detail, and a passion for delivering high-quality code 
Adaptability to changing project requirements and priorities 
Full proficiency using Git 
A degree in computer science, software engineering, or a related field 



