About the job
About Us: TABOU1 is a music NFT distribution platform. We sell digital and physical goods. Our catalog is growing rapidly as we onboard labels and artists and expanding in many genres. We provide a great alternative to streaming platforms for artists and music fans



We are looking for a passionate and motivated Junior Full-Stack Developer to join our team and grow with us. If you love coding, enjoy solving challenges, and want to make a real impact, you might be the person we’re looking for.



Position Overview:



As a Junior Full-Stack Developer, you’ll work closely with our Technical Lead to enhance, optimize and expand our web application. You’ll be directly contributing to the development of new features, improving existing ones, and ensuring high performance across the board. This is a great opportunity to grow your skills and be part of an exciting project.



Responsibilities:



· Collaborate with the Technical Lead to develop, improve, and maintain our web application.

· Implement new features and optimize existing ones to ensure the application’s scalability and performance.

· Work with NextJS to deliver high-quality web pages with excellent user experiences.

· Utilize Tailwind CSS to style and design responsive, modern interfaces.

· Manage content using Sanity.io (our CMS) and ensure efficient data flow.

· Handle static file storage using AWS S3.

· Deploy and manage the application on Netlify.

· Work with Retool to create, manage, and improve the dashboard for data management.

· Actively participate in team meetings, provide new ideas, and contribute to improving our processes.

· Write clean, maintainable, and well-documented code.



Requirements:



· Solid knowledge of JavaScript and basic understanding of NextJS or similar frameworks (React).

· Familiarity with Tailwind CSS or a strong desire to learn and work with it.

· Experience or interest in working with CMS platforms like Sanity.io.

· Basic understanding of RESTful APIs and front-end/back-end development principles.

· Experience in Web3 projects

· Enthusiasm for learning and growing in a collaborative team environment.

· Strong communication skills and the ability to contribute to technical discussions.

· Must speak English, French and Russian would be a nice plus



Nice to Have:



· Experience with AWS S3 for static file storage.

· Familiarity with deployment on Netlify.

· Understanding of Retool for creating and managing data dashboards.

· Experience or knowledge in relational databases, especially Postgres.

· Knowledge of best practices for performance optimization and scalability.

· Experience or knowledge in music streaming platform's architecture



What We Offer:



· A supportive, collaborative work environment with a team that values learning and growth.

· Opportunities to work on exciting projects that will challenge and expand your skill set.

· Flexible working hours, remote work.

· Competitive salary and benefits.

· The chance to be part of a project that has a real impact.



How to Apply:



If you’re an enthusiastic developer who’s eager to learn, grow, and contribute to a great project, we’d love to hear from you!



Please send your CV and a brief introduction about why you’d be a great fit for this role to jules.cremaschi@tabou1.com.