About the job
At Cula, we build the digital infrastructure for the growing global carbon removal economy to reach its full potential. Scaling carbon removal is one cornerstone to successfully fight climate change. We provide carbon removal facilities with a sophisticated operations management and tracking solution. This enables seamless and accurate tracking of carbon removal processes while simultaneously bringing tangible transparency into carbon removal certificates. Our platform connects with verification, certification, and financing stakeholders and by that helps our customers focus on what's most important: Remove CO2 for good. Our rapidly growing customer base does so successfully all over the globe.

‍

We are a growing team with a tech base located in Potsdam/Berlin and remote members from all over Europe. We are all makers at heart and care deeply about the quality of our work. What unites us is relentless execution and focus on the daily challenges our customers face, that can be solved with high quality software. We believe that tackling these will enable the carbon removal industry to scale to its needed capacity.



What you'll do



Build an offline-first web app that is deeply embedded and used on-site at carbon removal facilities to track carbon removal processes and emissions occurring along the way
Integrate time series machine data from industrial reactors and IoT sensors as supporting evidence for carbon removal activities
Architect automated ML-aided pipeline infrastructure and user facing apps to process data quickly at large scale
Develop protocols and APIs connecting key players in the carbon economy to exchange information faster and more reliable, increasing effectiveness of the whole system.
‍

Tech we use



Vue3 frontend styled with Tailwind
IndexedDB for local first capabilities
Containerized NestJS backend
TimescaleDB for time series data
Google Cloud Platform for hosting
NX Monorepo 
Github Actions for CI/CD
‍

What we are looking for



We don’t expect you to have a background in everything we use, but we do expect Typescript fundamentals and some practice working with frontend frameworks such as React or Vue and server side application technologies such as NestJs and SQL. 

‍

Your experience doesn’t matter as much as your drive and passion to learn quickly with your peers in a startup environment. You can pick a problem and solve it with high quality considering roadmap timelines. You consolidate your team or acquire new skills for everything you need along the way.

‍

You have great attention to detail. You care about the last pixel during frontend development and don’t sacrifice scalable and maintainable architecture during backend development. You are direct in your communication. You are clear about what you are doing, why, and what you expect of others. You live an open feedback culture, seeking the most fitting, unbiased solution for a given set of constraints.



What we offer



Challenging work while helping solving climate change
Great autonomy & agency in shaping a purposeful product
Opportunity to join on-site operation at carbon removal facilities around the world
Fair salary
Equity compensation
Regular team events & offsites
Hybrid work mode
Paid co-working space/desk near you, if required.

