About the job
Mission

Cuinti is introducing a new and 10x more effective way for companies to train their sales teams. Our mission is to be the first to automate the entire sales training process by creating technology that delivers deep knowledge, realistic practice, and tailored feedback that feels genuinely human. In doing so, we aim to make hands-on sales training accessible at scale for businesses, while elevating the growth journey for employees to a level previously only possible with a personal coach.



As a Technical Founder Associate / Junior Developer, you will support our co-founders in improving the product and building our platform that empowers thousands of employees from companies like Audi, Allianz, and AXA. You'll gain hands-on experience across all aspects of the product while learning from experienced founders.



Cuinti is backed by some of the best angel investors in Europe.



What You’ll Do

Direct Impact on Core Features: Work with our CTO on the development and refinement of our conversational AI system, focusing on solving challenging technical and user-experience problems.
Amaze our Users: Work closely with our amazing customers to understand their needs and help translate them into technical features, learning to bridge the gap between technical and business stakeholders.
Support AI Model Development: Gain experience in fine-tuning large language models, helping the team meet specific business needs and evaluate performance through testing.
Innovate with the Team: Contribute fresh ideas in a highly collaborative environment, directly impacting product direction and company strategy.


Tech Stack

Python, Github, Docker, Twilio, Redis, MongoDB, Huggingface, Azure, and more. With freedom to heavily influence our choice of tooling.



Who You Are

Early Career Developer: You have experience building applications in Python (internships, projects, or a junior role), and are looking for the opportunity to learn in a fast-paced, real-world environment.
Fast Learner: You have a passion for learning new technologies and solving problems, and are excited to work on systems involving AI and data.
Technical Familiarity: You’ve dabbled in Python, Docker, or similar technologies, and are eager to deepen your knowledge of production-level development.
Based in Europe: Eligible to work remotely in Europe, whether you're in Germany, France, Spain, or anywhere else.
Business Minded: Ability to understand and translate business requirements into technical solutions.
Excellent Communicator: Strong interpersonal skills with the ability to explain complex technical concepts to non-technical stakeholders.


Nice to have

Some Frontend Exposure: Experience or interest in frontend technologies like React or other modern frameworks.
Familiarity with Machine Learning: A basic understanding or interest in machine learning and conversational AI.
Audio Data & Phone Systems Interest: Curiosity about audio data, phone systems, and related technologies (e.g., μ-law data or compression) is a plus.


Why join us?

High Impact & High Growth Role: Significant ownership from day 1 and the opportunity to grow with the company.
Flexible Remote Work: Fully remote startup with the freedom to work from anywhere in Europe and flexible working hours with a monthly remote work budget for co-working or equipment.
Personal Growth Budget: Annual allowance for conferences, courses, books, or subscriptions to foster your professional development.
Exciting Team Offsites: Regular strategy meetings in fantastic locations across Europe.
Performance-Based Bonus: Monthly bonuses in addition to your salary, rewarding your contributions and achievements.
Employee Stock Option Plan (ESOP): Opportunity to own a part of the company after having proven your impact


Who we are

We are Tim, Allegro & Jérôme. All of us have founded a company before and are passionate about building an amazing company with you as the first hire and corner piece of our team.

Commitment to Diversity and Inclusion

Even if the current team looks like it lacks diversity, we are very committed to building an inclusive environment where everyone feels welcomed and valued. We are convinced that this drives innovation and is the only way forward. We encourage applicants of all backgrounds, cultures, genders, abilities, and experiences to apply - and we mean it.


