About the job
Your mission

At sewts we automate what others can’t. Gripping of deformable materials like textiles is a task most humans see as intuitive and simple. However, this is a complicated task for robots as they lack the detailed and contextual understanding of where and with what level of sensitivity to handle these textiles. As deep-tech enthusiasts, we teach industrial robots human perception skills.

We are building a foundational technology stack called sewts.JUPITER. JUPITER uses genAI to simulate realistically the behavior of deformable & soft objects to create corresponding computer vision models and grabbing strategies. Based on our physical AI first time ever robots get enabled to handle soft & deformable materials. With over €10M in funding we will bring automation into all untapped industries, like cloth manufacturing, textiles handling, recycling & e-commerce.

You will make the difference! We have built a high-performance culture where efficient target achievement and consistent development is at the core of our company philosophy. We are working independently with ownership and a strong motivation to go the extra mile. We are setting our goals high, enjoying our daily challenges, while loving to share a laugh with our fellow team members. We are a diverse team, with many different nationalities, which values direct communication and open feedback.

As our new Intern Full Stack Development (m/f/d), you will be an integral part of our Software Team. You will be responsible for Frontend and Backend Development of our Software Platform focusing on enabling the robotic automation of deformable material handling. You will focus on providing the Backend infrastructure for our AI and computer vision solutions as well as working on the web frontend where Integrators and our hardware developers can easily develop the process and customize the AI and Vision software to their needs specific to each use case.

How You Will Create An Impact With Us

Develop the Web-Frontend of our Vision Platform in Vue.js;
Develop the Python Backend in Django for our Cloud hosted modelling and deployment user interface; 
Develop the Python Backend responsible for designing the computer vision process and deploying and running the generated AI software; 
Package and deploy software upgrades as well as tend to the runtime infrastructure from SW side. 

Your profile

You are studying Computer Science or in a similar field or already attained professional experience;
You are experienced in Python, HTML, CSS and Javascript;
You have basic experiences in Vue.js or similar Web Frameworks like AngularJS or React.

Why us?

Be a part of a leading robotics and automation startup in Munich and leave an impact from day one;
Benefit from our Remote Work Policy, where you spend ≥70% of your time in the office with your team members and ≤30% in Mobile Office;
Engage in regular team events (e.g., barbecues, summer parties, ski trips and laser tag);
Develop your career through regular feedback cycles through weekly and quarterly check-ins.

Your Talent Partner

We want to ensure a smooth recruitment process for you. If you have questions or would like to know more about this role, your Talent Partner, Fatima, is there to support you.

You may use the following channels to connect with her:

Email: fatima.sakhawat@sewts.de

WhatsApp: 0049 1577 744 4352

About Us

At sewts we are automating complex processes by teaching robots human-like perception skills. We are a young, ambitious, and diverse team of eight different nationalities with the mission to become the global go-to Partner for automated processing of deformable and soft materials. We are always willing to push our boundaries to reach our goals and targets, while learning from the daily challenges of an emerging startup. We are always on a hunt for likeminded individuals who are passionate about robotics automation, AI and courageous to create an impact. Are you ready?

