About the job
The world’s electricity production and consumption is quickly changing to adapt to a net zero future. To support this renewable future, our power grids need to adapt. Endre tech is a startup originating from Chalmers University of Technology in data science, AI and electric power engineering. At Endre we develop tools, forecasts and analytics to help electric power grid operators plan for, and build, the future grid. Using state-of-the-art AI and data science technologies we make sure the the future power grid can support a renewable-based future. We are a company driven by impact, and are looking for similar people.



As a Frontend Developer at endre, you won’t just be coding—you’ll be crafting the user experience. Without a dedicated UI designer, you'll lead the creation of intuitive, user-centered interfaces from scratch. This role offers the freedom to shape the design and user experience of our platform in a fast-paced, creative environment. You'll work closely with our team and clients to turn complex power grid data into clear, engaging visualizations, ensuring a seamless user experience.



What we offer:

At endre tech we provide a creative atmosphere in a purpose-driven environment where the ability to influence both the company and the service is high.

We work together in a very tight team and strongly believe in the power of helping and sharing ideas, knowledge and insights with our colleagues and with our community of customers and partners.



Key responsibilities:

Design, develop, and maintain a responsive frontend for our SaaS platform.
Take full responsibility for crafting user-centered experiences, translating complex requirements into intuitive designs.
Create impactful data visualizations using libraries like Typescript echarts.
Develop prototypes or full-scale features efficiently, whether through coding or design tools, depending on your approach.
Lead UI/UX efforts, making key decisions about how our users interact with the platform in the absence of a dedicated UI designer.


About you:

To excel in this role, we believe you:

Have a degree in software engineering, interaction design, IT, or a related field.
Are proficient in JavaScript, React, GitHub, and have experience with RESTful APIs.
Have a strong understanding of UX and UI design principles and are excited about taking the lead on design work.
Enjoy building user-centered experiences from the ground up and have a passion for coding and design.
Are able to work independently, taking ownership of both design and development.


Nice-to-have experience (not required):

TypeScript.
Apache Echarts.
Tailwind
Zustand
Python
FastAPI
Figma
A portfolio showcasing previous projects.




We look forward to hearing from you!