About the job
About Reonic:



At Reonic, we’re on a mission to transform the renewable energy landscape through cutting-edge software solutions for solar, storage, charging, and heat pumps. We are committed to delivering an all-in-one sales tool tailored specifically for Installers and Utilities, ensuring that we provide the best possible solutions for their businesses.



With a community of over 500 customers and the support of visionary investors, we’re rapidly scaling our impact in this dynamic industry. We're looking for passionate, motivated Junior Engineers to join our team in Augsburg and be a part of this exciting journey.



Together, let’s harness the power of innovation to drive sustainable change and create a greener future!



What you will do:



Contribute to the development and enhancement of our B2B SaaS products primarily contributing across our feature rich frontends.
Create intuitive and beautiful components using React, Typescript, and Tailwind CSS
Participate in the creation of world class User Experiences for our market
Contribute to the overall look and feel of the web application alongside Product and Design team


You will be perfect for the role if you have:



Minimum of 12 months of Software Development experience, preferably in a startup environment or a Product focused scale-up
Genuine interest renewable energy (we ask for context here)
Self-starter mindset to be responsible for your own learning
Ownership: We're a small team, so everyone has to be an owner. Taking accountability and ownership is baked into our DNA
Drive: We value conscientious people, we work hard and we play hard.
Product mindset. You enjoy delighting your customer
Side projects, OSS or notable achievements outside of "work"


Why you should join us:



A pivotal role in a fast-growing VC-backed startup building a product already loved by 500 paying B2B customers
An opportunity for personal and professional growth
Freedom to try new things and make quick changes (nothing-is-impossible spirit of a small but effective team)
Competitive salary package
Plus the obvious: Gym membership, coffee, regular team events, MacBook & more


Ready to make an impact in the renewable energy sector? Send us your application. We’re excited to work together on simplifying renewable technology access.



Please always feel encouraged to send us your application even if you may think you don’t fulfil all the criteria (yet).