We are a team of entrepreneurs, therapists, and engineers bringing joy back to therapy. At PlaynVoice, we are reshaping mental health care by combining AI with clinical expertise to make documentation a breeze. In just six months, our AI scribe has gone from concept to reality, gaining 100+ users in Switzerland and Germany. We are generating over 1,000 patient notes monthly. We are looking for entrepreneurs. Fast, ambitious, and smart individuals who want to take care of the people who take care of our mental health.

Tasks
You are our first tech hire and will be working closely with our CTO and the founding team. As part of our dynamic team, you’ll be instrumental in scaling our SaaS products and shaping the future of AI in psychotherapy. We need someone with hands-on experience in building SaaS applications.

Take ownership of features and drive implementation across the backend and frontend
Adapt the latest AI models (language and speech) and techniques to our use case
Data-Driven Development: Use data to inform decisions, design experiments, and validate product features, ensuring continuous improvement and innovation
Requirements
Passion for AI innovation and a desire to make a meaningful impact in healthcare
A solid track record of performance in software engineering (ideally in a SaaS start-up)
Familiarity with Python, Cloud infrastructure, and experience in AI applications
Strong understanding of full-stack development, ideally FastAPI and MongoDB
Benefits
Be part of a mission-driven, fast paced start-up that has a positive impact on our health
Flexible, remote-first work environment; Learn from experienced founders and advisors
Equity in a high-growth company
To apply please send your CV and 5-10 sentences about your motivation. Applications without motivation to join PlaynVoice will be ignored!

