About the job
Location Zurich

Type 6-Month Contract

About The Role

Our client in the pharmaceutical industry is looking for a Full Stack Developer to support an exciting project that focuses on improving manufacturing processes. This role involves helping to create an automated recommendation system that uses machine learning to find ways to make manufacturing smoother and more efficient. The goal is to give manufacturing experts and operators useful insights to guide their work.

Key Responsibilities

 Backend Development
 Build and maintain backend processes, mainly for handling data and running SQL-based tasks.
 Work with Databricks (experience is a plus but not required).
 Frontend Development
 Develop simple and clear web-based user interfaces with HTML, CSS, and JavaScript.
 Use Plotly for data visualizations to make information easy to understand for users.
 Scripting and Automation
 Write Python scripts using common libraries like scikit-learn, pandas, and numpy to automate tasks and support machine learning processes.
 API Development
 Create straightforward APIs to make data accessible across different parts of the system.
 Quality Assurance
 Perform unit testing to check that the code works reliably and without errors.
 Documentation
 Clearly document code, workflows, and processes to make future maintenance easier.
 Collaboration
 Work closely with the team to integrate machine learning models with other data tools (experience in machine learning is a bonus).

Qualifications

 Able to work independently and meet deadlines reliably.
 Experience working in an agile setup; familiarity with Jira is a plus.
 Strong problem-solving skills with close attention to detail.

Why Apply?

This 6-month contract offers the chance to work on a meaningful project within the pharmaceutical sector, impacting real-world manufacturing processes through technology. It’s ideal for a developer with a mix of backend and frontend skills who enjoys making data-driven solutions.

By applying for this position, I consent to the Swisslinx Group of companies

 storing my personal information (including name, contact details, Identification and CV information etc.) on their internal or external servers for the purpose of informing me of potential employment opportunities
 using my personal information or
 supplying it to third parties upon express consent for the purpose of informing me of potential job opportunities
 transferring where applicable my personal information to a country outside the EEA/EFTA

I also hereby agree to the Swisslinx privacy policy (http//www.swisslinx.com/en/legal/privacy-policy) and Terms of Use (http//www.swisslinx.com/en/legal/disclaimer)

