Optum is a global organization that delivers care, aided by technology to help millions of people live healthier lives. The work you do with our team will directly improve health outcomes by connecting people with the care, pharmacy benefits, data and resources they need to feel their best. Here, you will find a culture guided by diversity and inclusion, talented peers, comprehensive benefits and career development opportunities. Come make an impact on the communities we serve as you help us advance health equity on a global scale. Join us to start Caring. Connecting. Growing together


Software Engineer needs to perform Technical work in PLSQL, JAVA , DROOLS , REACT and CICD Pipeline for NEMIS project deliveries.


Software engineering is the application of engineering to the design, development, implementation, testing and maintenance of software in a systematic method. The roles in this function will cover all primary development activity across all technology functions that ensure we deliver code with high quality for our applications, products and services and to understand customer needs and to develop product roadmaps.


These roles include, but are not limited to analysis, design, coding, engineering, testing, debugging, standards, methods, tools analysis, documentation, research and development, maintenance, new development, operations and delivery. With every role in the company, each position has a requirement for building quality into every output. This also includes evaluating new tools, new techniques, strategies; Automation of common tasks; build of common utilities to drive organizational efficiency with a passion around technology and solutions and influence of thought and leadership on future capabilities and opportunities to apply technology in new and innovative ways.


Primary Responsibilities:

Basic, structured, standard approach to work
Comply with the terms and conditions of the employment contract, company policies and procedures, and any and all directives (such as, but not limited to, transfer and/or re-assignment to different work locations, change in teams and/or work shifts, policies in regards to flexibility of work benefits and/or work environment, alternative work arrangements, and other decisions that may arise due to the changing business environment). The Company may adopt, vary or rescind these policies and directives in its absolute discretion and without any limitation (implied or otherwise) on its ability to do so
Required Qualifications:

Undergraduate degree or equivalent experience
Full Stack ( PLSQL, JAVA , DROOLS, REACT, SPRINGBOOT ) , He/she should have good knowledge on Agile and Github. They should have good understanding in AI/ML and Cloud

At UnitedHealth Group, our mission is to help people live healthier lives and make the health system work better for everyone. We believe everyone–of every race, gender, sexuality, age, location and income–deserves the opportunity to live their healthiest life. Today, however, there are still far too many barriers to good health which are disproportionately experienced by people of color, historically marginalized groups and those with lower incomes. We are committed to mitigating our impact on the environment and enabling and delivering equitable care that addresses health disparities and improves health outcomes — an enterprise priority reflected in our mission.

