About the job
acemate is on a mission to democratize access to personalized education. Our AI learning platform transforms uploaded documents into exams, mind maps, and more, providing university students with a personalized learning experience and real-time feedback. We also help educators automate content creation and enhance engagement, partnering with leading German universities – including TU Munich, RWTH Aachen, and TU Berlin. Built by founders with previous experience at BCG, Antler, BMW, SAP and N26, we have secured pre-seed funding and are excited to find new team members to join our mission.

Tasks

As a Founding Product Engineer, you will play a critical role in shaping the direction and technology of our company. This role offers a unique opportunity to work closely with Jan (CTO) and Paul (CPO) and scale a product from the ground up. We will treat you as a core member of the team from day 1 and you will be incentivized as such.

In this role, you will:

Spearhead the development of new features in Next.js, from ideation to deployment
Engage directly with users to uncover pain points and improve the product experience
Leverage product data to derive insights that optimize our user flows and boost monetization
Build growth-focussed features that drive virality and community engagement
Improve UX/UI design using Tailwind


To give you a better overview, here are some of the past projects you would have contributed to:

Enhanced the onboarding workflow to drive user activation and retention
Built AI flashcard functionality as core feature
Implemented freemium monetization and optimized pricing tiers based on usage data
Overhauled our landing page to increase conversion


Requirements

Bachelor’s or higher degree in Computer Science, Engineering, or a related field
2+ years of experience in full-stack development
Strong background in Next.js (or at least React)
Optional: Experience with Tailwind CSS, PostgreSQL/Supabase, gen-AI applications (esp. Vercel AI SDK), UI/UX, web analytics tools and testing frameworks
Entrepreneurial spirit with a strong sence of ownership and superb problem-solving skills
Obsessed with understanding user behavior and needs
Fluent in either English or German


Benefits

Competitive salary package with equity component
Working in a small but driven team built around performance and learning
Flexible environment with high degree of autonomy and option to work remotely
Team events and acemate parties! :)


Desired Skills and Experience
Product Management

Full-Stack Development

Web Development

Next.js

React

Tailwind CSS

Supabase

PostgreSQL

Vercel AI SDK

TypeScript

JavaScript

UI/UX