As a Full Stack Developer at SmartStamp, you will be responsible for reprogramming our app using Flutter and leading our front-end development efforts. This opportunity is ideal for creative individuals passionate about making a mark in the art market through innovative technology. Suitable for creative graduate/undergraduate students or professionals with field experience looking for a dynamic startup environment.

Gain unparalleled leadership experience and insights in the art-tech sector, enhancing your resume and opening doors to future career opportunities. The role is voluntary and does not offer financial compensation for the first 6 months.

Tasks
Develop mobile applications using Flutter, ensuring cross-platform compatibility and high performance.
Optimise our applications for scalability and UI/UX integrity.
Implement automated workflows, collaborating closely with our product management and sales teams.
Lead, mentor, and motivate your team members, fostering collaboration and high-performance.
Requirements
Strong skills in Flutter, React, TypeScript, NodeJS, and Firebase, with a foundational understanding of Web3 and Solidity.Experience with WordPress, basic PHP knowledge, and iOS native development capabilities.
Enrolled in or completed a Bachelor’s degree in a related field, or equivalent experience, with strong problem-solving and multitasking abilities.
Excellent communication, organizational skills, and a portfolio demonstrating previous front-end development projects.
Benefits
Invaluable Experience: Gain firsthand exposure to the dynamics of the art market.
Flexible and Remote Work: Adapt your schedule to balance academic, personal, and project commitments, with the option to work comfortably from home.
Growth and Networking: Collaborate with experts in both tech and art, broadening your skills and professional connections.
Based on our success, a financial compensation package will be offered.
We are looking forward to your application!