%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{wasysym}
\usepackage{lastpage}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{fontawesome5}

\newcommand{\portfoliosymbol}{\faFolderOpen\hspace{-.1em}\faBriefcase}

\pagenumbering{arabic}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Venkata Sai Yakkshit Reddy Asodi}~\href{https://www.cedzlabs.com/yakkshit}{\vspace{1pt}}\\
    Kungsmarkvågen 71 37144. \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +46 0793550685 ~ \href{mailto:saiyakkshit2001@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  {saiyakkshit2001@gmail.com}} ~ 
    \href{https://linkedin.com/in/yakkshit/}{\raisebox{-0.2\height}\faLinkedin\ {yakkshit}}  ~
    \href{https://cedzlabs.com/yakkshit}{\raisebox{-0.2\height}\faRss\ {yakkshit}}  ~
    \href{https://github.com/saiyakkshit}{\raisebox{-0.2\height}\faGithub{ saiyakkshit}}
    \vspace{-8pt}
\end{center}
%-----------EDUCATION-----------
\section{Summary}
Highly motivated and detail-oriented computer science student with a strong foundation in programming languages, software development, and cloud computing. Currently pursuing a Bachelor's degree in Computers at the Blekinge Institute of Technology, with a focus on Python, Java, and AI. Completed certifications in MTA-Python and Java, AI-Intern, and GCP Cloud Carrier Path. Demonstrated expertise in developing projects utilizing RESTful APIs, JSON, Google Cloud services, and deploying applications on Google Home and Google Hub devices.


% As a tech enthusiast currently pursuing a Bachelor's degree in Computers at the Blekinge Institute of Technology, I am equipped with a strong foundation in computer science and a passion for leveraging technology to drive innovation. With a focus on Python, Java, and AI, I have completed certifications such as MTA-Python and Java, AI-Intern, and GCP Cloud Carrier Path. My practical experience includes developing a Google Assistant using Google Cloud services and APIs, utilizing RESTful APIs and JSON for communication, and deploying apps on Google Home and Google Hub devices. By combining my technical skills with hands-on experience in AI engineering and Android app testing, I have gained proficiency in TensorFlow, OpenCV, and automation testing using tools like Appium. I am adept at collaborating within a team to enhance user experience and ensure web security. With a track record of successfully completing projects such as AWS file encryption and Langversation, an end-to-end encrypted multilingual chat-based Android application, I have demonstrated my ability to implement secure systems and leverage technologies like AWS KMS, S3, Firebase, and Kubernetes. Through my coursework and extracurricular involvement, I have developed strong leadership skills, multitasking abilities, and meticulous attention to detail. As I continue to explore emerging technologies like augmented reality and system administration, I am committed to continuous learning and leveraging my expertise to contribute to cutting-edge projects in the field of computer science.


 \vspace{-10pt}

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {BetaTesting, Inc}{Jan 2023 -- Present}
      {Android Application Tester}{Remote}\\
      \vspace{10pt}
      \textbf{Description:}
      I Have worked as a beta tester for the New App Launcher on Android Phones, identifying and reporting bugs to the development team, and developed problem-solving skills and attention to detail through this experience. I have also learned to work collaboratively with a team to improve user experience and web security.
      \vspace{-10pt}
      \textbf{Responsibilities:}
      \resumeItemListStart
        \resumeItem{Conducting beta testing for a new Android app launcher, identifying and reporting bugs to the development team.}
        \resumeItem{Utilizing Robo Script and Appium for automation testing of the application.}
        \resumeItem{Monitoring log reports and collaborating with the development team to improve user experience and web security.}
        \resumeItem{Utilizing Android Studio as the development environment to visualize and analyze the application.}
        \resumeItem{Leveraging Perfetto for system tracing and performance analysis.}
    \resumeItemListEnd
    \textbf{Environment:}\emph{Android app testing, bug reporting, problem-solving, collaboration, Android Studio, Appium.}


    

    \resumeSubheading
      {Cedzlabs.com}{May 2021 -- June 2022}
      {FullStack Engineer}{Remote}\\
      \vspace{10pt}
      \textbf{Description : }I was responsible for creating and maintaining both the front-end and back-end components of websites and web applications
as a full-stack engineer at CedzLabs. Working with a range of programming languages and technologies.\\
\textbf{Responsibilities : }
      \vspace{-5pt}
      \resumeItemListStart
        \resumeItem{Created and maintained both front-end and back-end components of websites and web applications, ensuring seamless user experiences.}
        \resumeItem{Utilized a range of programming languages and technologies including HTML, CSS, JavaScript, Node.js, React, and SQL databases.}
        \resumeItem{Designed website interfaces using HTML and CSS for visually appealing and responsive layouts.}
        \resumeItem{Implemented JavaScript to add functionality and interactivity to the websites.}
        \resumeItem{Hosted websites using the npm (Node.js) server to ensure smooth deployment and accessibility.}
        \resumeItem{Integrated various APIs to enhance the functionality and features of the websites.}
        \resumeItem{I have also done SEO Optimization for a good ranking of the website.}
        \resumeItem{Monitored website performance using also the Google search console, Google Analytics, and crashes using Firebase Performance SDK.}\\

      \resumeItemListEnd
\vspace{0.5pt}
\textbf{Environment:}\emph{HTML, CSS, JS, TypeScript, PHP, SQL, React, JSON, ML, Firebase, GCP.}





    \resumeSubheading
      {VERZEO.INC}{Aug 2020 -- Mar 2021}
      {AI Engineer Intern}{Remote}\\
      \vspace{10pt}
      \textbf{Description : }This Python project uses computer vision and a deep learning model to detect face masks in images and videos. It can identify
individuals wearing masks and those who are not and can be integrated into real-time face mask detection systems.\\
\textbf{Responsibilities : }
      \vspace{-5pt}
      \resumeItemListStart
        \resumeItem{Developed a Python project utilizing computer vision and deep learning models to detect face masks in images and videos.}
        \resumeItem{Utilized TensorFlow for training the model to accurately identify individuals wearing masks and those who are not.}
        \resumeItem{Integrated the trained model into a real-time face mask detection system using the OpenCV library and its computer vision capabilities.}
        \resumeItem{Conducted rigorous testing to ensure the accuracy of the face mask detection system.}
        \resumeItem{Worked with a provided dataset and implemented the project in Python, TensorFlow, OpenCV, and deep learning.}\\

      \resumeItemListEnd
\vspace{0.5pt}
\textbf{Environment:}\emph{Python, TensorFlow, OpenCV, Deeplearning.}
  \resumeSubHeadingListEnd
    
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{}{AWS File Encryption}} $|$ \emph{Python, Selenium, AWS Cloud Console}}{January 2023}\\
          \vspace{9pt}
          \textbf{Description:}
          The project involved using AWS KMS and S3 to encrypt and decrypt files securely. A unique key is generated using KMS to
encrypt files, and the same key is used to decrypt them, with access controls implemented using IAM to ensure authorized
access.
          \vspace{-8pt}
          \resumeItemListStart
            \resumeItem{Designed and implemented a secure file encryption/decryption system using AWS KMS and S3, with access controls enforced through IAM.}
            \resumeItem{Utilized AWS KMS and S3 to encrypt and decrypt files, generating unique keys for secure access. Implemented access controls through IAM to ensure authorized access.}
            \resumeItem{Successfully implemented a secure and scalable file encryption/decryption system, improving data security and access control for the organization.}
          \resumeItemListEnd
          \textbf{Tools:}\emph{ AWS KMS, S3, encryption, decryption, unique key, access controls, IAM, secure files.}
          \vspace{-18pt}
          \resumeProjectHeading
          {\textbf{\href{https://github.com/saiyakkshit/Langversation}{Langversation}} $|$ \emph{CI/CD, Android Studio}}{December 2022}\\
          \vspace{6pt}
          \textbf{Description:}
          Langversation is a communication, end‑to‑end encrypted multilingual chat‑based android application which was developed in kotlin. This removes the language barrier between two users. where the data used to store in the Firebase. which was being monitered in Google Analytics after the Deployment of the Application for the users.
          \vspace{-8pt}
          \resumeItemListStart
            \resumeItem{In the development of user conversation i have used XML as front end and Kotlin for the back end.}
            \resumeItem{For the storage and authentication which was used in the app was done in FirebaseStorage and FirebaseAuthentication.}
            \resumeItem{Ml kit translational API which was used to convert from one language to the other.}
            \resumeItem{The Performance and Crashes of the App was monitered using the Firebase Performance SDK and Firebase Crashlytics SDK.}
          \resumeItemListEnd 
          \textbf{Tools:}\emph{
Kotlin, java, ML kit, Firebase, XML.}
        \vspace{-18pt}
          
          \resumeProjectHeading
          {\textbf{\href{https://github.com/saiyakkshit/}{Random Feed}} $|$ \emph{CI/CD, Android Studio}}{December 2022}\\
          \vspace{9pt}
          \textbf{Description:}
          Random Feed which was developed in the Flutter framework for both Ios and Android which used to showcase the Random posts and chat with the posts in the form of comments. The data is being processed at GCP by using the ml models and RESTful API.
          \vspace{-8pt}
          \resumeItemListStart
            \resumeItem{Implemented a machine learning model using TensorFlow Lite on Google Cloud Platform.}
            \resumeItem{Utilized the Flutter framework for app development and integrated various APIs.}
            \resumeItem{Designed the user interface using Adobe XD.}
            \resumeItem{The authentication was done using Firebase Service.}
            \resumeItem{The Applications is monited by using the Firebase Tools.}
          \resumeItemListEnd 
          \textbf{Tools:}\emph{
Dart, Android, IOS, ML kit, Firebase, GCP.}

    
    \vspace{-18pt}
      \resumeProjectHeading
          {\textbf{\href{https://github.com/saiyakkshit/}{Networking and Firewalls}} $|$ \emph{Bash, Ubuntu}}{November 2022}\\
          \vspace{10pt}
          \textbf{Description:}
           I utilized bash scripting and Ubuntu to establish communication between networked devices. I employed HTTP requests to enable data transfer between these devices, and set up firewall rules to ensure secure communication.
           \vspace{-8pt}
          \resumeItemListStart
            \resumeItem{Established communication between networked devices using bash scripting and Ubuntu.}
            \resumeItem{Employed HTTP requests for data transfer and set up firewall rules to ensure secure communication.}
            \resumeItem{Updated firewall rules to establish a secured connection between client and server.}
            \resumeItem{Successfully designed and implemented a secure network communication system, improving data transfer capabilities and ensuring the security of sensitive information.
Tools: Bash scripting, Ubuntu OS, HTTP requests, Firewall rules.}
           
          \resumeItemListEnd 
          \textbf{Tools:}\emph{Bash scripting,
Ubuntu OS,
HTTP requests,
Firewall rules.}
          \vspace{-18pt}
          \resumeProjectHeading
          {\textbf{\href{https://www.cloudskillsboost.google/public_profiles/6bf05c97-e7a5-48b7-bd37-03938dae9743/badges/2357183}{DevOps Essentials in Google Cloud}} $|$ \emph{CI/CD, Google Cloud Console}}{June 2022}\\
          \vspace{9pt}
          \textbf{Description:}
          I have gained hands-on experience and helped them improve in areas such as Cloud Source Repositories, Kubernetes Engine, Load Balancers, and troubleshooting workloads on GKE. Using DevOps in GCP.
          \vspace{-8pt}
          \resumeItemListStart
            \resumeItem{Utilized Cloud Source Repositories, Kubernetes Engine, Load Balancers, and troubleshooting workloads on GKE to improve DevOps practices in GCP.}
            \resumeItem{Used cloud repositories with Git for version control.}
            \resumeItem{Managed deployments using Kubernetes Engine, scaling and managing containers for common scenarios.}
            \resumeItem{Deployed Kubernetes Load Balancer Service with Terraform, setting up a Kubernetes cluster and deploying Nginx service on it.}
            \resumeItem{Deployed and configured a continuous delivery pipeline using Jenkins on Kubernetes Engine.}
          \resumeItemListEnd 
          \textbf{Tools:}\emph{
Terraform, Kubernetes, Nginx, Jenkins, DevOps.}
    
    \vspace{-12pt}
    \resumeProjectHeading
          {\textbf{\href{https://www.cloudskillsboost.google/public_profiles/6bf05c97-e7a5-48b7-bd37-03938dae9743/badges/2346814}{Deploying an app in Kuberneties}} $|$ \emph{CI/CD, Google Cloud Console}}{June 2020}\\
          \vspace{9pt}
          \textbf{Description:}
          We have used the app to deploy Kubernetes on Gcp which helped in reliability, scalable, and efficiency while also providing a
consistent deployment model that helps the streamline development and deployment process.
          \vspace{-8pt}
          \resumeItemListStart
            \resumeItem{Deployed Kubernetes on GCP for reliability, scalability, and efficiency in the deployment process.}
            \resumeItem{Created Kubernetes clusters and used Docker for containerization.}
            \resumeItem{Used YAML manifests to deploy applications in Kubernetes.}
            \resumeItem{Deployed and serviced manifests to the Kubernetes cluster using kubectl, and exposed the application to the internet using Kubernetes Ingress.}
          \resumeItemListEnd 
          \textbf{Tools:}\emph{
Kubernetes, Docker, Google Cloud Platform.}
    \resumeSubHeadingListEnd
\vspace{-10pt}
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Deployment/Automation/templating tools : }{Terraform, Jenkins, Docker, Bitbucket/Gitlab CI/CD pipeline.} \\
     \textbf{Developer Tools : }{Unity, AWS, Google Cloud Platform, Android Studio, Perfetto.} \\
     \textbf{Technologies : }{ GitHub. Github Workflows.} \\
     \textbf{Frameworks : }{Django, TensorFlow, Nodejs, HTTP, SpringBoots, Flutter, Threejs, RESTful API.}\\
     \textbf{Languages : }{ Python, Dart, Go, Java, C, HTML, JS, SQL,TypeScript, Command Line Tools(Shell scripting, Linux).}\\
     \textbf{Testing Tools : }{Firebase Performance, Firebase Testing, Unit testing, System Tracing. }\\
    }}
 \end{itemize}
%-----------EDUCATION-----------
\section{Education Details}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Blekinge Institute of Technology}{Sep. 2022 -- Present}
      {Bachelor of Science in Computer Science}{Valhallavägen 1, 371 41 Karlskrona.}
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading
      {University College Of Engineering Jntuk}{Aug. 2019 -- Jun. 2022}
      {Bachelor of Science in Computer Science}{Kakinada, AndhraPradesh, India 533003.}
  \resumeSubHeadingListEnd

%


%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-4pt, parsep=3pt]
                \item\small Data Structures
                \item Software Methodology
                \item Algorithms Analysis
                \item Database Management
                \item Network Slicing
                \item Internet Technology
                \item Systems Programming
                \item Computer Architecture \\
                \item Kubernetes
                \item Tensorflow
                \item Argumented Reality
                \item System Administration\\
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

%-----------INVOLVEMENT---------------
\section{Certificates / Achivements}
            \resumeItemListStart
                \resumeItem{\href{https://portal.certiport.com/Portal/Pages/PrintTranscriptInfo.aspx?action=Cert&id=395&cvid=ej8fNHXiWfEntRn/kBIQHw==}{I have Achieved
                MTA(Microsoft Technical Associate)-Python}}
                \vspace{-7pt}
                \resumeItem{\href{https://drive.google.com/file/d/1dhl67D-8GIbrHul7yOXaZnMi9Wy8rkg4/view}{I have Completed as a AI - Intern at Verzeo.inc}}
                \vspace{-7pt}
                \resumeItem{\href{https://portal.certiport.com/Portal/Pages/PrintTranscriptInfo.aspx?action=Cert&id=398&cvid=QiBkzVlVnojF0hDdRTf01Q==}{I have Achieved
                MTA(Microsoft Technical Associate)-Java}}
                \vspace{-7pt}
                \resumeItem{\href{https://www.cloudskillsboost.google/public_profiles/6bf05c97-e7a5-48b7-bd37-03938dae9743}{I have Achieved a Skill badges at Google Cloud carrier path}}
                
                
                
            \resumeItemListEnd
    \vspace{-8pt}


%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular / Contributions}
            \resumeItemListStart
                \resumeItem{Led a chapter of 30+ members to work towards goals that improve and promote CedzLabs community service, academics, and unity.}
                \vspace{-7pt}
                \resumeItem{I contributed to Kubernetes is Developed new functions in the release script to ensure a smooth and error-free release process by checking dependencies, generating release notes and uploading the final tarball to a remote storage location.}
                \vspace{-17pt}
                \resumeItem{I have contributed to adding a new class, MicroK8sClusterUpgradeEvent, to the MicroK8sCluster and implemented upgrade logic to handle it for performing necessary upgrade logic for the MicroK8s cluster.}
                \vspace{-7pt}
                \resumeItem{I have been currently working on my thesis as we have deployed the webxr  Argumented reality into the web which is based on threejs engine and Android application based on Arcore and which is being deployed into the cloud using GCP and the load balancers and monitoring of a load of both the application and the web using Kubernetes and cloud watch and terraform for the automation.}
                
                
            \resumeItemListEnd
    \vspace{-8pt}
    \textbf{Strengths : }\emph{Leadersip skills,
Multitasking,
Attention to details.
}
\end{document}
